---
title: "LVMwR Chapter 3"
author: "Can Mekik"
date: "2018-03-30"
output: 
  html_notebook:
    toc: true
    toc_depth: 5
---

# Setup

Dependencies: foreign, psych, lavaan (v0.5-15; use devtools)

```{r}
performance.data <- foreign::read.spss("performance.data.sav")
performance.data <- as.data.frame(performance.data)
performance.data <- subset(performance.data,
                           select=c("ags1", "ags2", "ags3", "ags4",
                                    "ags5", "ags6", "ags7", "ags8",
                                    "ags9", "ags10", "ags11", "ags12"))
# make variables accessible without reference to performance.data
attach(performance.data)
```

# Normality

```{r}
psych::mardia(performance.data)
```

Test stats and qqplot suggest data are not normal.

# Models

Try both standard ML and alternative approaches.

## 4 Factor Models

```{r}
achievement.goal.cfa4.model <- "
  map =~ ags1 + ags5 + ags7
  mav =~ ags2 + ags6 + ags12
  pap =~ ags3 + ags9 + ags11
  pav =~ ags4 + ags8 + ags10
  "
```


### Maximum Likelihood

```{r}
achievement.goal.cfa4.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                         data=performance.data)
lavaan::summary(achievement.goal.cfa4.fit, fit.measures=T, standardized=T)
```

Poor fit.

#### $\chi^2$ Corrections

Perhaps poor fit due to $\chi^2$ statistic used on non-normal data. Try corrections.

##### Satorra-Bentler

```{r}
achievement.goal.cfa4.satorra.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                                 data=performance.data,
                                                 test="Satorra.Bentler")
lavaan::summary(achievement.goal.cfa4.satorra.fit, 
                fit.measures=T, standardized=T)
```


##### Yuan-Bentler

```{r}
achievement.goal.cfa4.yuan.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                              data=performance.data,
                                              test="Yuan.Bentler")
lavaan::summary(achievement.goal.cfa4.yuan.fit, 
                fit.measures=T, standardized=T)
```

##### Bollen-Stine

```{r}
achievement.goal.cfa4.bollen.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                                data=performance.data,
                                                test="Bollen.Stine")
lavaan::summary(achievement.goal.cfa4.bollen.fit, 
                fit.measures=T, standardized=T)
```

##### Results

Still poor fit.

### WLS

```{r}
achievement.goal.cfa4.wls.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                             data=performance.data,
                                             estimator="WLS")
lavaan::summary(achievement.goal.cfa4.wls.fit, 
                fit.measures=T, standardized=T)
```

Still poor fit.

### DWLS

```{r}
achievement.goal.cfa4.dwls.fit <- lavaan::cfa(achievement.goal.cfa4.model,
                                             data=performance.data,
                                             estimator="WLSMV")
lavaan::summary(achievement.goal.cfa4.dwls.fit, 
                fit.measures=T, standardized=T)
```

Yay! Better/good fit.

## 3 Factor Models

So achieved good fit with 4 factors, will 3 factors do as well?

Lump together `mav` and `map` as `mastery`.

```{r}
achievement.goal.cfa3.model<-'mastery=~ags1+ags2+ags5+ags6+ags7+ags12
pap=~ags3+ags9+ags11
pav=~ags4+ags8+ags10'
```

Since DWLS worked, use that.

### DWLS

```{r}
achievement.goal.cfa3.dwls.fit<-lavaan::cfa(achievement.goal.cfa3.model, 
                                            data=performance.data, 
                                            estimator="WLSMV")

lavaan::summary(achievement.goal.cfa3.dwls.fit, fit.measures=T, standardized=T)
```

## 2 Factor Models

Now consider 2 Factors

Lump together `pap` and `pav` as `performance`.

```{r}
achievement.goal.cfa2.model<-'
mastery=~ags1+ags2+ags5+ags6+ags7+ags12
performance=~ags3+ags4+ags8+ags9+ags10+ags11'
```

Since DWLS worked, use that.

### DWLS

```{r}
achievement.goal.cfa2.dwls.fit<-lavaan::cfa(achievement.goal.cfa2.model,
                                            data=performance.data,
                                            estimator="WLSMV")

lavaan::summary(achievement.goal.cfa2.dwls.fit, fit.measures=T, standardized=T)
```

# Comparisons

Compare models using ANOVA.

## 3 vs 2 factors

```{r}
lavaan::anova(achievement.goal.cfa3.dwls.fit, achievement.goal.cfa2.dwls.fit)
```


## 4 vs 2 factors

```{r}
lavaan::anova(achievement.goal.cfa4.dwls.fit, achievement.goal.cfa2.dwls.fit)
```


## 4 vs 3 factors

```{r}
lavaan::anova(achievement.goal.cfa4.dwls.fit, achievement.goal.cfa3.dwls.fit)
```

